---
title       : BMI Calculator
subtitle    : Pitch
author      : Saul Grimaldo
job         : Consultant
framework   : html5slides       # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## What is a BMI?
BMI, or Body Mass Index, is:

1.A proxy for body fat percentage

2.Most useful for people with a sedentary lifestyle. 

3.Not reliable for taller people

---

## Body Mass Index Calculator

I created an app that helps people calculate their own BMI, using the BMI formula:

$$\frac{weight}{height^2}$$

Where weight is in kilograms and height is in meters.

You can find the app in: 

https://sgrimald89.shinyapps.io/DataProducts/

---

### Example- How to use the application

You weigh 150 lbs and are 5 feet 8 inches

1.Choose to enter your data in the Imperial system using the pulldown box.

2.Enter your height and weight (150 lbs and 5.667 feet) into their respective boxes.

3.Hit "Calculate BMI" and you're DONE!

---
### How it works

First, R will convert your height and weight into the metric system (if they're not already metric), and then R will calculate the BMI using your metric system measurements using the following:

```{r, echo=FALSE}
height = 5.667/3.28084
weight = 150/2.20462
```
```{r, echo=TRUE}
BMI = weight / (height*height)
```

Thus R will evaluate this example to:

```{r,echo=FALSE}
weight / (height*height)
```

---

### What your BMI means:

1. If your BMI is less than 18.5, then you're likely underweight.

2. If your BMI is within the 18.5-24.9 range, you are likely in a normal weight.

3. If your BMI is within the 25-29.9 range, you are likely overweight. 

4. If your BMI is higher than or equal to 30, you are likely obese.

NOTE: These classifications are true only if you have an average lifestyle.

THANK YOU!